Breakable Elastic-plastic Constraint for\\Rigid Body Simulation

### 2017-08-07 pdocs/thesis/epj-jcgt.tex
Box2D implementation in jcgt article

\paragraph{Changes to define maximum forces}

\paragraph{Neutral position update}

\paragraph{Debugging tools}

>>>>

\paragraph{Changes to processing} 
In addition to allowing definition of maximum forces and moment during initialization 
b2ElasticPlasticJoint allows definition of maximum moment by giving maximum elastic rotation.

For each step maximum rotational impulse and linear impulses are calculated using step length and 
current orientation of the joint.

During solution phase impulse is clamped so that it does not too big.
If clamping is activated additional processing is done at the beginnig of next step to update neutral position and
increment plasticity values.

\paragraph{Debugging tools} 
Box2D testbed offers many useful tools and only few additions were made for testing of plasticity.
\begin{enumerate}
\item Tunable visualization of joint forces
\item Numerical output of joint forces as absolute values and as percentage of maximum forces
\item Numerical output of usage of plastic capacity
\item Selection of joints for display of numerical values
\end{enumerate}
